\documentclass[draft]{jfp}

\let\Bbbk\relax

\journaltitle{JFP}
\cpr{Cambridge University Press}
\doival{10.1017/xxxxx}

\lefttitle{Submitted for publication.}
\righttitle{Journal of Functional Programming}

\totalpg{\pageref{lastpage01}}
\jnlDoiYr{2021}

\usepackage{multicol}
\usepackage{xparse}
%\usepackage[capitalise,noabbrev]{cleveref}
%\usepackage{xcolor}
\usepackage{mathtools}
\usepackage{wasysym}
\usepackage{agda}
\usepackage{tex/agdadimmed}
\usepackage{newunicodechar}
\usepackage{mdframed}
\usepackage{wrapfig}
\usepackage{boxedminipage}
\usepackage{dsfont}
\usepackage{etoolbox}
\usepackage{natbib}

\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{stmaryrd}
\usepackage{scalerel}
\usepackage{multirow}

\usepackage{tikz}
\usetikzlibrary{positioning,fit,calc}
\tikzset{block/.style={draw, thick, text width=3cm, minimum height=1.5cm, align=center}, line/.style={-latex}}
\usepackage{pgfplots} 
\newcommand{\todo}[1]{\textcolor{red}{\textbf{#1}}}


\DeclareRobustCommand{\VAN}[3]{#3}


%% 
%% %include agda.fmt
%% %include fmts/polycode.fmt 
%% %include fmts/agdabase.fmt
%% %include fmts/agda.fmt
%% %include fmts/syntax.fmt
%% %include fmts/misc.fmt
%%

%%
%% Agda typesetting commands shorthands, for
%% manual typesetting of inline code
%%

\newcommand{\af}{\AgdaFunction}
\newcommand{\un}{\AgdaUnderscore}
\newcommand{\ad}{\AgdaDatatype}
\newcommand{\ab}{\AgdaBound}
\newcommand{\ac}{\AgdaInductiveConstructor}
\newcommand{\aF}{\AgdaField}
\newcommand{\as}{\AgdaSymbol}
\newcommand{\ak}{\AgdaKeyword}
\newcommand{\ap}{\AgdaPrimitiveType}
\newcommand{\an}{\AgdaNumber}
\newcommand{\aC}{\AgdaComment}
\newcommand{\am}{\AgdaModule}


%%
%% Unicode for typesetting Agda code
\input{tex/unicode.tex}

%%
% Multi-column code
\NewDocumentCommand{\vcodesep}{}{{\color{lightgray}\vrule}}

% displays put some stuff like code in a paragraph, without interrupting it.
\setlength{\parskip}{0em} 
\setlength\mathindent{0.2cm}
%\setlength\abovedisplayskip{0em}
%\setlength\belowdisplayskip{em}
\usepackage{float}
\newcommand{\displayskip}[1]{%
  {\parskip=0pt\parindent=0pt\par\vskip #1\noindent}}
\NewDocumentCommand{\display}{m}
  {{\ifhmode%
    \parskip=0pt\parindent=0pt\par\vskip 5pt\noindent
    %\displayskip{\abovedisplayskip}%
    %\displayskip{0pt}%
       #1%
    %\displayskip{\belowdisplayskip}%
    \parskip=0pt\parindent=0pt\par\noindent
    \displayskip{0pt}%
   \else
     #1
   \fi}}

\NewDocumentCommand{\twocodes}{O{0.49\textwidth} O{0.49\textwidth} m m}
  {\display{\vskip -10pt
    \begin{minipage}[t]{#1}
    #3
    \end{minipage}
    \hfill\vcodesep
    \begin{minipage}[t]{#2}
    #4
    \end{minipage}
  }}

\begin{document}
\raggedbottom

%% Title information
\title{Hefty Algebras: Modular Elaboration of Higher-Order Effects}
% 
% %% Author with single affiliation.
% \author{Cas van der Rest}				
% \orcid{0000-0002-0059-5353}            
% \affiliation{
%   \institution{Delft University of Technology}          
%   \city{Delft}
%   \country{The Netherlands}                  
% }
% \email{c.r.vanderrest@tudelft.nl}       
% 
% \author{Casper Bach Poulsen}			
% \orcid{0000-0003-0622-7639}            
% \affiliation{
%   \institution{Delft University of Technology}          
%   \city{Delft}
%   \country{The Netherlands}                  
% }
% \email{c.b.poulsen@tudelft.nl}    
%

\begin{authgrp}
\author{Casper Bach Poulsen}
\affiliation{Delft University of Technology\\
  (\email{c.b.poulsen@tudelft.nl})}
\author{Cas van der Rest}
\affiliation{Delft University of Technology\\
  (\email{c.r.vanderrest@tudelft.nl})}
\end{authgrp}

\begin{abstract}
  Algebraic effects and handlers is an increasingly popular approach to
  programming with effects.  An attraction of the approach is its modularity:
  effectful programs are written against an interface of declared operations,
  which allows the implementation of these operations to be defined and refined
  without changing or recompiling programs written against the interface.
  However, higher-order operations (i.e., operations that take computations as
  arguments) break this modularity.  While it is possible to encode higher-order
  operations by elaborating them into more primitive algebraic effects and
  handlers, such elaborations are typically not modular.  In particular,
  operations defined by elaboration are typically not a part of any effect
  interface, so we cannot define and refine their implementation without
  changing or recompiling programs.  To resolve this problem, a recent line of
  research focuses on developing new and improved effect handlers.  In this
  paper we present a (surprisingly) simple alternative solution to the
  modularity problem with higher-order operations: we modularize the previously
  non-modular elaborations commonly used to encode higher-order operations.  We
  demonstrate how our solution scales to define a wide range of known
  higher-order effects from the literature, and develop modular higher-order
  effect theories and modular reasoning principles that build on and extend the
  state of the art in modular algebraic effect theories.  All results are
  formalized in Agda.
\end{abstract}

% 
% \keywords{
%   Type Safety,
%   Modularity,
%   Reuse,
%   Definitional Interpreters,
%   Dependently Typed Programming
% } %% \keywords are mandatory in final camera-ready submission
% 

\maketitle

\input{tex/sections/1-introduction.tex}
\input{tex/sections/2-algebraic-effects.tex}
\input{tex/sections/3-hefty-algebras.tex}
\input{tex/sections/5-examples.tex}
\input{tex/sections/4-laws.tex}
\input{tex/sections/6-related.tex}
\input{tex/sections/7-conclusion.tex}
% 
\paragraph*{Acknowledgements}
We thank the anonymous reviewers for their comments which helped improve the exposition of the paper.
  Furthermore, we thank Nicolas Wu, Andrew Tolmach, Peter Mosses, and Jaro Reinders for feedback on earlier drafts.
  This research was partially funded by the NWO VENI Composable and Safe-by-Construction Programming Language Definitions
project (VI.Veni.192.259).

\label{lastpage01}

%% Bibliography
\bibliographystyle{JFPlike}
\bibliography{tex/references}

\end{document}
